Demes: a standard format for demographic models

### 2022-08-03 paper.tex
Tweak from review

A primary design goal of Demes is to provide a means of
unambiguously communicating the results of demographic
model inferences to population genetic simulators.
Since demography is defined in terms of groups of individuals
and these groupings are influenced by genetics,
it is difficult to find a simple definition that separates
the two. Thus, we have attempted to be pragmatic,
limiting the features that we include in Demes to
those that are (or can reasonably be expected to)
in practise regarded as part of a demographic model.

>>>>

A primary design goal of Demes is to provide a means of
unambiguously communicating the results of demographic
model inferences to population genetic simulators.
Since demography is defined in terms of groups of individuals
and these groupings are influenced by genetics,
it is difficult to find a simple definition that separates
the two. Thus, we have attempted to be pragmatic,
limiting the features that we include in Demes to
those that are in practise regarded as part of a demographic model.
